Measurement of a dwarf galaxy rotational velocity from its Lyman-alpha line emission

### 2015-09-22 paper/letter.tex
simple paragraph describing rotation results

%----------------------New commands -------------------
\newcommand{\hb}{H$\beta$}
\newcommand{\ha}{H$\alpha$}
\newcommand{\oiii}{[OIII]}
\newcommand{\oii}{[OII]}
\newcommand{\nii}{[NII]}
\newcommand{\esca}{erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$}
\newcommand{\esc}{erg cm$^{-2}$ s$^{-1}$}
\newcommand{\es}{erg s$^{-1}$}
\newcommand{\esa}{erg s$^{-1}$}
\newcommand{\kms}{km s$^{-1}$}
\def\simgt{\lower.5ex\hbox{\gtsima}}
\def\simlt{\lower.5ex\hbox{\ltsima}}
%------------------------------------------------------

@@

3. Rotation and the expected features.

>>>>

%----------------------New commands -------------------

\newcommand{\tol}{TOL1214-277}
\newcommand{\hb}{H$\beta$}
\newcommand{\ha}{H$\alpha$}
\newcommand{\oiii}{[OIII]}
\newcommand{\oii}{[OII]}
\newcommand{\nii}{[NII]}
\newcommand{\esca}{erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$}
\newcommand{\esc}{erg cm$^{-2}$ s$^{-1}$}
\newcommand{\es}{erg s$^{-1}$}
\newcommand{\esa}{erg s$^{-1}$}
\newcommand{\kms}{km s$^{-1}$}
\def\simgt{\lower.5ex\hbox{\gtsima}}
\def\simlt{\lower.5ex\hbox{\ltsima}}
%------------------------------------------------------

@@

3. Rotation and the expected features.
It has been shown that rotation also imprints an effect on the
Lyman-alpha morphology. 
The most important consequence of rotation is that spherical 
symmetry is broken.
The line morphology now depends on the viewing angle respect to the
rotation axis.  
For a line sight perpendicular to the rotation axis the intensity and
the line center and the line width increase with rotational velocity. 
When the rotational velocity is close to the half-line width of the
static line, the line becomes single peaked as it is observed in
\tol, a unique feature that other theoretical models find
impossible to reproduce.
